Metrics

### 2023-12-11 src/plots.Rmd
Add exploratiomn cod plot

>>>>

Display a plot of cases by cause of death.

# Format plot data
ecoddata <- df %>%
    filter(is_agreed == TRUE) %>%
    group_by(physician_cghr10) %>%
    summarize(count = n()) %>%
    mutate(
        cod_label = paste0(
            physician_cghr10,
            "\n(n=", count, ", ",
            if_else(
                ((count / nagree) * 100) < 1,
                "<1",
                as.character(round((count / nagree) * 100))
            ), "%)"
        )
    ) %>%
    arrange(count) %>%
    mutate(
        cod_label = factor(cod_label, levels = unique(cod_label))
    )

# Plot the data
ecodplot <- ecoddata %>%
    ggplot(aes(x = cod_label, y = count)) +
    geom_bar(
        stat = "identity",
        fill = "#1d1d1d",
        color = "white",
        width = 0.5
    ) +
    labs(
        y = y_title,
        x = element_blank()
    ) +
    theme_minimal() +
    theme(
        panel.grid = element_blank(),
        axis.title.x = element_text(margin = margin(t = 10)),
        axis.title.y = element_text(margin = margin(r = 10))
    ) +
    coord_flip()

# Save the plot
ecodplot
ggsave("../manuscript/fig-data-cod.pdf", plot = ecodplot, dpi = 300)
```
